Tigth Bounds for Online Balanced Graph Partitioning

### 2020-05-08 paper/disc20clustering.tex
Intro continuation

\maciek{Practical motivation}

@@

\subsubsection{Learning model.}

We consider a variant of Online Balanced Partitioning, where communication requests are permanent: once a pair of nodes start communicating, they continue forever.
To avoid infinite cost, each communicating pair must be collocated.
We study instances with finite cost: we assume that the communication graph can be perfectly partitioned in the clusters (no external requests are required).
The algorithm's goal is to \emph{learn} the communication graph, and partition it without too many reconfigurations.

\noindent
\textbf{Adversarial input and the competitive analysis.}
\maciek{The competitive ratio definition and the worst case inputs}

\noindent
\textbf{Challenges.}
The partitioning model has a rent-or-buy dilemas. The decision, what to evict is present in both models.

>>>>

We study a problem of managing the virtual machines in a data center.
We focus on the scenario where virtual machines can be migrated during runtime to another physical machine.
The possibility of migration allows reacting to unpredictable communication patterns.
For example, if some distant virtual machines communicate often, it is vital to reduce their distance to save network bandwidth.
The objective is to~minimize the total network bandwidth used for communication and for migration.

Intuitively, we would like to minimize inter-machine
interactions by mapping frequently communicating virtual machines to the same physical machine
Since communication patterns change over time, the~placement of virtual machines should be managed in an online manner, by migrating them between physical machines.
The~objective is to minimize the weighted sum of inter-machine communication and repartitioning costs.
The former is defined as the number of communication requests between virtual machines placed at distinct physical machines, and the latter as the number of migrations.

@@

\noindent
\textbf{Learning model.}
We study a variant of Online Balanced Partitioning, where communication requests are permanent: once a pair of nodes start communicating, they continue forever.
To avoid infinite cost, each communicating pair must be collocated.
We study instances with finite cost: we assume that the communication graph can be perfectly partitioned in the clusters (no external requests are required).
The algorithm's goal is to \emph{learn} the communication graph, and partition it without too many reconfigurations.
We refer to this problem variant as the \emph{learning} problem.

\medskip 
In both models we assume that the communication patterns are not known in advance to our algorithm.
We measure the~quality of~presented algorithmic solutions by competitive analysis~\cite{borodin-book}, which is well-suited for problems that are online by their nature.
In the competitive analysis, the goal is to~optimize \emph{the competitive ratio} of a given online algorithm: the ratio of its cost to the cost of~an~optimal offline algorithm that knows the whole input sequence in advance.
